### 2015-10-08 untitled.tex
edited untitled.tex

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.9\columnwidth]{figures/example}
\caption{An illustrative example demonstrating a deadline miss at time $22$ under the period enforcer algorithm.
\label{fig:example}%
}
\end{center}
\end{figure}

@@

>>>>

@@

One may consider to enrich the period enforcer with the following power: when the processor becomes idle, the task becomes ready to run right away regardless of the settings of eligibility time. Even with this, the above example remains valid by introducing a lowest priority task $\tau_3$ with execution time $C_3=13$ (to be executed from $3$ to $9$ and $13$ to $20$) and $T_3=D_3=100$.
